Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-11-18 talk/pepm2011/paper.tex
copyright data
add related work. now we are at 11 pages again.

%
\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}
%
\begin{document}
\conferenceinfo{PEPM}{'11, Austin, USA}
\CopyrightYear{2011}
\copyrightdata{[to be supplied]} % XXX

@@

@@

Partially known data structures are built directly into Prolog (via unbound
logic variables) and thus the treatment of partially static data structures
was part of partial evaluation of Prolog programs from the early stages
\cite{lloyd_partial_1991}. One effect of unfolding in Prolog is that terms that
are constructed and immediately matched again, completely disappear in the
residual program. This is similar to what our optimization does for an
imperative language.
In functional programming this idea was introduced as
 constructor specialisation by Mogensen \cite{mogensen_constructor_1993}.
\reva{I'd refer here to \cite{wadler_deforestation:_1988}
  and \cite{gill_short_1993}}
\revb{cite and relate to: boxing analysis}

>>>>

%
\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}
%
\begin{document}
\conferenceinfo{PEPM'11,} {January 24--25, 2011, Austin, Texas, USA.}
\CopyrightYear{2011}
\copyrightdata{978-1-4503-0485-6/11/01}

@@

% XXX insert "practical" somewhere

@@

Partially known data structures are built directly into Prolog (via unbound
logic variables) and thus the treatment of partially static data structures
was part of partial evaluation of Prolog programs from the early stages
\cite{lloyd_partial_1991}. One effect of unfolding in Prolog is that terms that
are constructed and immediately matched again, completely disappear in the
residual program. This is similar to what our optimization does for an
imperative language.
In functional programming this idea was introduced as
 constructor specialisation by Mogensen \cite{mogensen_constructor_1993}.

A related optimization is also that of deforestation
\cite{wadler_deforestation:_1988,gill_short_1993} which tries to remove
intermediate lists or trees in functional languages. More explicitly geared at
optimizing boxing is boxing analysis \cite{jrgensen_calculus_1996} which tries
to fully remove pairs of calls to box/unbox in a functional language.
